\bibliographystyle{IEEEtran}
\begin{thebibliography}{99}

\bibitem{ros2_ref}
ROS 2 Documentation, ``Overview,'' Available: \url{https://docs.ros.org/en/rolling/}. Accessed: Dec. 15, 2025.

\bibitem{urdf_ref}
ROS Wiki, ``Unified Robot Description Format (URDF),'' Available: \url{https://wiki.ros.org/urdf}. Accessed: Dec. 15, 2025.

\bibitem{yaml_ref}
YAML Language Specification, ``YAML Ain’t Markup Language,'' Available: \url{https://yaml.org/spec/}. Accessed: Dec. 15, 2025.

\bibitem{dsl_ref}
Wikipedia, ``Domain-specific language,'' Available: \url{https://en.wikipedia.org/wiki/Domain-specific_language}. Accessed: Dec. 15, 2025.

\bibitem{roswiki_urdf}
ROS Wiki, ``URDF,'' Available: \url{https://wiki.ros.org/urdf}. Accessed: Dec. 15, 2025.

\bibitem{ros2docs_urdf}
ROS 2 Documentation, ``URDF Tutorials,'' Available: \url{https://ros.ncnynl.com/en/humble/Tutorials/Intermediate/URDF/URDF-Main.html}. Accessed: Dec. 15, 2025.

\bibitem{industrial_training_urdf}
ROS-Industrial Training, ``Introduction to URDF,'' Available: \url{https://industrial-training-master.readthedocs.io/en/melodic/_source/session3/Intro-to-URDF.html}. Accessed: Dec. 15, 2025.

\bibitem{wikipedia_urdf}
Wikipedia, ``Unified Robot Description Format,'' Available: \url{https://en.wikipedia.org/wiki/URDF}. Accessed: Dec. 15, 2025.

\bibitem{rep105}
REP-105: Coordinate Frames for Mobile Platforms, ROS Enhancement Proposal. Available: \url{https://www.ros.org/reps/rep-0105.html}. Accessed: Dec. 15, 2025.

\bibitem{rep120}
REP-120: Standard Units of Measure and Robot Model Representation, ROS Enhancement Proposal. Available: \url{https://www.ros.org/reps/rep-0120.html}. Accessed: Dec. 15, 2025.

\bibitem{rep199}
REP-199: URDF Inertial Specification, ROS Enhancement Proposal. Available: \url{https://www.ros.org/reps/rep-0199.html}. Accessed: Dec. 15, 2025.

\end{thebibliography}